\textbf{Using the MSU Thesis Class}

### 2022-12-15 docs/msu-thesis.tex
v4.0b fixes size of the degree box on the title pages.

\def\msuversion{4.0}
\def\msudate{2022/12/13}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics, Languages, and Cultures\\Michigan State University\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version \msuversion\\\msudate}
\usepackage{fontspec}
\usepackage[lmargin=.75in,rmargin=.75in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{titling}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf,small]{titlesec}
\usepackage[section]{placeins}
\usepackage[colorlinks=true]{hyperref}
\setmonofont{Inconsolatazi4}

@@

\section{Acknowledgements}
Thanks to Lars Madsen, Ulrike Fischer and Peter Wilson for help with setting up parts of the memoir code for versions 1.0--1.4 (now eliminated due to changed requirements). Thanks to Wolfgang Sternefeld for supplying the \pkg{linguex}\ spacing fix code, Leo Liu for the landscape page numbering code, which greatly simplified my original version. Thanks to Florent Chervet for early \pkg{hyperref} code (up until v.3.6), and Ulrike Fischer for the current \pkg{hyperref} code.  Thanks also to the following students who have reported problems over the years: Irina Agafonova, Ali Al-jiboory, Abubakr Ayesh, Julian Blank, Dmitriy Bryndin, Greg Christian, Kyle Crayne, Ciaron Hamilton, Matt Husband, Changkuk Jung, Claire Kopenhafer, Adam Liter, Vanessa Maldonado, William Muir, Alicia Parrish, Neil ver Planck, Nick Rekuski, Giacomo Romanini, William Sands, Adam Soliman, Erik Stitt,  Eremey Valetov, Matthew Vincent, Michael Wojcik, Stephen Yowono, Ali Zare, and Yisu Zhou. A special thank you to Non Thongprong who graciously provided a copy of his entire thesis which allowed me to debug some especially subtle spacing inconsistencies.

>>>>

\def\msuversion{4.0b}
\def\msudate{2022/12/15}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics, Languages, and Cultures\\Michigan State University\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version \msuversion\\\msudate}
\usepackage{fontspec}
\usepackage[lmargin=.75in,rmargin=.75in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{titling}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf,small]{titlesec}
\usepackage[section]{placeins}
\usepackage[colorlinks=true]{hyperref}
\setmonofont{Inconsolatazi4}

@@

\section{Acknowledgements}
Thanks to Lars Madsen, Ulrike Fischer and Peter Wilson for help with setting up parts of the memoir code for versions 1.0--1.4 (now eliminated due to changed requirements). Thanks to Wolfgang Sternefeld for supplying the \pkg{linguex}\ spacing fix code, Leo Liu for the landscape page numbering code, which greatly simplified my original version. Thanks to Florent Chervet for early \pkg{hyperref} code (up until v.3.6), and Ulrike Fischer for the current \pkg{hyperref} code.  Thanks also to the following students who have reported problems over the years: Irina Agafonova, Ali Al-jiboory, Abubakr Ayesh, Julian Blank, Dmitriy Bryndin, Greg Christian, Kyle Crayne, Ciaron Hamilton, Matt Husband, Changkuk Jung, Claire Kopenhafer, Adam Liter, Vanessa Maldonado, William Muir, Eureka Pai, Alicia Parrish, Neil ver Planck, Nick Rekuski, Giacomo Romanini, William Sands, Adam Soliman, Erik Stitt,  Eremey Valetov, Matthew Vincent, Michael Wojcik, Stephen Yowono, Ali Zare, and Yisu Zhou. A special thank you to Non Thongprong who graciously provided a copy of his entire thesis which allowed me to debug some especially subtle spacing inconsistencies.
